\section{Conclusion}
\label{src:conclusion}
In this paper, we described our study on the need for
changes in
the existing OpenSHMEM memory model to enable users in
utilizing
the different available kinds of memory on emerging tiered
memory architectures. We motivated this change
by illustrating the missing features in OpenSHMEM for
supporting Intel KNL processors with different memory
configurations.
%We then introduced a new feature called \texttt{Symmetric
%Memory partitions} in OpenSHMEM and
We then proposed the runtime
changes with its associated new routines %associated with this feature
for
supporting different kinds of memory using a new feature in
OpenSHMEM called \texttt{Symmetric Memory Partitions}.
We implemented
symmetric memory partitions on Cray SHMEM as
\texttt{SHMEMX} prefixed features without breaking
backward compatibility and any performance regression.
We validated our implementation with ParRes kernels on Intel
KNL processors, for which we received a close to 25\%
improvements on using MCDRAM compared to using DDR.

The basic traits proposed for symmetric memory partitions
are based on our best estimate for supporting emerging tiered
memory systems. In future work, we will build on the proposed
features and include other additional types of memory like
persistent memory and constant memory. Moreover, our early
performance analysis are performed on kernels with the
entire memory fitting into one single kind. In future, we will
also test on bandwidth bound applications with requirement
for more than one kind of memory.
