\section{Introduction}
\label{src:intro}

Emerging systems support multiple kinds of memory with different
performance and capacity characteristics. %Examples of
Systems with
multiple kinds of memory are seen in recent architectures such as
AMD Fiji, NVIDIA Pascal, and Intel Knights Landing. The latest
Many Integrated Core (MIC) processor, the Intel Xeon Phi,
code-named Knights Landing (KNL)~\cite{KNL}, combines the traditional
off-package DDR memory with the increased high bandwidth on-package
memory called as the Multi-Channel DRAM~\cite{MCDRAM} (MCDRAM). %MCDRAM
%offers high bandwidth (up to 4X more than DDR4) with limited
%capacity (up to 16GB).
To identify and manage different kinds of memory,
vendors provide their own programming approaches
%for users to identify the different kinds of memory
using external libraries like CUDA~\cite{cuda} and
Memkind~\cite{memkind}.
Applications can also use low level programming approaches.
Irrespective of the selection, these approaches limit application
portability. To address this problem, programming libraries such as
%In response, it is for the programming library interfaces like
OpenSHMEM~\cite{osm} must provide a more consistent and portable
interface for accessing different kinds of memory on tiered memory systems.

In this paper, we define a set of OpenSHMEM runtime changes and routines
to support different kinds of memory for the symmetric heap. During
program execution, the current
OpenSHMEM memory model creates the symmetric heap with specific
memory characteristics that are determined by the implementation.
The runtime changes described in this paper would allow users to
determine a region on which the symmetric heap can be created. We call this
user-determined region as \emph{Symmetric Memory Partition}. To define
their characterisitcs, each memory partition features a list of traits, with 
%to define their
%characteristics
memory kind being one of those featured traits.

The major contributions of this work are:
\begin{itemize}
    \item proposing a set of new runtime changes and routines in
    OpenSHMEM to support different kinds of memory on tiered memory
    systems;
    \item implementation of the proposed changes in
    Cray SHMEM~\cite{csma} for Intel KNL processors as an example
    use-case for memory partitions on emerging systems;
    % a vendor-specific OpenSHMEM implementation
    %from Cray Inc;
    \item performance regression analysis on creating multiple
    symmetric partitions; and
    \item performance analysis of the proposed changes using
    Parallel Research Kernels (ParRes)~\cite{parres}.
\end{itemize}

This paper is organized as follows.
Section~\ref{src:bground} provides a brief overview for Cray SHMEM
and Section~\ref{src:knl} describes Intel KNL architecture with its
different modes of memory configuration. Section~\ref{src:mmodel}
illustrates the current OpenSHMEM memory model and necessitates the need
for changes in the existing memory model. In Section~\ref{src:smempart}
we propose the new symmetric memory partition feature and in
Section~\ref{src:implement} we follow up with
the implementation of the proposed features in Cray SHMEM.
Section~\ref{src:regression} provides details of the performance
regression analysis with the implementation and in
Section~\ref{src:perf}
we use ParRes OpenSHMEM kernels to present the performance benefits on
determining the kind of memory for creating the symmetric heap. We
discuss related work in Section~\ref{src:relate} and conclude in
Section~\ref{src:conclusion}.
